\begin{acknowledgements}

The research included in this thesis could not have been performed if not for the assistance, patience, and support of many individuals.  I would first like to extend my deepest gratitude toward my advisor Dr. Claudio Campagnari for his mentorship and constant confidence over the course of my undergraduate studies. It was he who suggested that I study rare Higgs decays, the latter half of this thesis. He also introduced me to Dr. David Stuart, under whose advisement the former half of this thesis was performed. Claudio's support, generosity, and boundless wisdom has made me a better student and physicist.

I would additionally like to thank Dr. David Stuart. His versatile mind and constant effort to encourage learning led me to be more curious and thoughtful. Furthermore, his understanding and amiable treatment of his students promoted a positive environment for learning and practicing physics.

I would also like to extend my appreciation to Dr. Indara Suarez for believing in me and for her continual guidance as well as to Nick Amin, Bennett Marsh, and Sicheng Wang for their companionship and for helping me with anything and everything.

This research would not have been possible without the assistance of the CMS experimental collaboration who constructed the experimental apparatus and built the foundations for the data analysis.  

Finally I would like to extend my deepest thanks to my parents Orlando and Cynthia Guiang without whose love, support and understanding I could never have completed this undergraduate degree, nor would I have had the confidence or inspiration to pursue research in physics.

\end{acknowledgements} 